Design Principles from Glass Sponges \\for Structurally Robust Lattices

### 2018-12-07 Paper-FernandesWeaverBertoldi_AdvMaterials_2018.tex
added figs in supplemental
.

To understand  the role of the sponge architecture, we start by comparing its performance to that of other three 2D lattices, all based on a   square architecture with edges of length $L$ (see Supplementary Materials for details). Specifically,  we  consider:
\emph{Design A}  which is inspired by the sponge and comprises a set of double diagonals going in opposite directions (see \cref{Fig2}(a)); \emph{Design B}  which is similar to the sponge design but only contains a single diagonal crossing each of the closed cells (see \cref{Fig2}(b));   \emph{Design C}  which is similar to bracings found in modern structural engineering and contains a crossing set of diagonal beams in every cell (see \cref{Fig2}(c)); and \emph{Design D}  which  has no diagonal reinforcement (see \cref{Fig2}(d)). In all our designs we consider struts with rectangular cross section and depth large enough to avoid any out-of-plane deformation. Moreover, to ensure a fair mechanical comparison between the four designs, we keep the total mass constant and
for \emph{Designs A, B}, and \emph{C} we also constrain the  ratio between the mass of the diagonals and non-diagonals struts to be identical (see Supplementary Materials for details).  %Finally, in all our analyses we constraint the lattices to deform in-plane. To this end, in our experiments we consider specimens sufficiently thick for which out-of-plane deformation is negligible and in the the numerical simulations we assume plane-strain conditions.

We started by testing samples of the four considered designs comprising
a tessellation of $6\times6$ square cells with $L=1.91$ cm. The samples were fabricated with a multi-material 3D printer \mf{(add model @James)} using \KB{name of material} \mf{add info here @James} and compressed uniaxially  using  an Instron Model 5969 with 50kN capacity  (\Cref{Fig2}(e)). \KB{switch labels (f) and (e) in Fig 2} %Using this set-up, we tested three replicas of each design that were 3D printed and tested on different days.
The results reported in \Cref{Fig2}(f)  show that all structures are characterized by an initial linear behavior, a sudden departure from linearity caused by in-plane buckling and catastrophic failure following immediately thereafter.   Furthermore, it is also important to note that all  designs with diagonal reinforcement (i.e. \emph{Designs A-C}) overlay each other in the linear regime. Focusing on the initial linear regime, we find that  the different diagonal reinforcement designs considered do not impact the structure's overall stiffness (i.e. the initial stiffness of Designs A, B and C is identical). Design D, as expected, has a higher stiffness because of its thicker vertical and horizontal element's. However, it fails much earlier due to a shorter critical buckling strain. On the other hand, \emph{Design A} (the sponge design) outperforms the  considered structures in the amount of load it can bare before the onset of buckling occurs and provides the best mechanical performance without compromising the structural stiffness.

>>>>

To understand the role of the sponge architecture, we start by comparing its performance to that of additional three 2D lattices, all based on a square architecture with edge lengths $L$ (see Supplementary Materials for details). Specifically,  we  consider:
\emph{Design A}  which is inspired by the sponge and comprises a set of double diagonals going in opposite directions (see \cref{Fig2}(a)); \emph{Design B}  which is similar to the sponge design but only contains a single diagonal crossing each of the closed cells (see \cref{Fig2}(b));   \emph{Design C} which is similar to bracings found in modern structural engineering and contains a crossing set of diagonal beams in every cell (see \cref{Fig2}(c)); and \emph{Design D}  which  has no diagonal reinforcement (see \cref{Fig2}(d)). In all our designs we consider struts with rectangular cross section and depth large enough to avoid any out-of-plane deformation. Moreover, to ensure a fair mechanical comparison between the four designs, we keep the total mass constant and
for \emph{Designs A, B}, and \emph{C} we also constrain the  ratio between the mass of the diagonals and non-diagonals struts to be identical (see Supplementary Materials for details).  %Finally, in all our analyses we constraint the lattices to deform in-plane. To this end, in our experiments we consider specimens sufficiently thick for which out-of-plane deformation is negligible and in the the numerical simulations we assume plane-strain conditions.

We began our analysis by testing samples of the four considered designs comprising a tessellation of $6\times6$ square cells with $L=1.91$ cm. The samples were fabricated with a multi-material 3D printer \mf{(add model @James)} using \KB{name of material} \mf{add info here @James} and compressed uniaxially  using  an Instron Model 5969 with 50kN capacity  (\Cref{Fig2}(e)). \KB{switch labels (f) and (e) in Fig 2} %Using this set-up, we tested three replicas of each design that were 3D printed and tested on different days.
The results reported in \Cref{Fig2}(f)  show that all structures are characterized by an initial linear behavior, a sudden departure from linearity caused by in-plane buckling and catastrophic failure following immediately thereafter.   Furthermore, it is also important to note that all  designs with diagonal reinforcement (i.e. \emph{Designs A-C}) overlay each other in the linear regime. Focusing on the initial linear regime, we find that  the different diagonal reinforcement designs considered do not impact the structure's overall stiffness (i.e. the initial stiffness of Designs A, B and C is identical). Design D, as expected, has a higher stiffness because of its thicker vertical and horizontal element's. However, it fails much earlier due to a shorter critical buckling strain. On the other hand, \emph{Design A} (the sponge design) outperforms the  considered structures in the amount of load it can bare before the onset of buckling occurs and provides the best mechanical performance without compromising the structural stiffness.
